Radiocarbon measurement of CO~2~ from carbonate minerals using a gas ion source with an open split interface

### 2021-10-27 doc/AMS-15/AMS-15_poster.Rmd
Add errors to tables

```{r}
library(tidyverse)
library(amstools)
library(hgis)
library(here)
library(gt)
library(Bchron)
library(gghighlight)
library(patchwork)
library(scales)
library(latex2exp)

options(digits = 3)
options(scipen = 4)
options(decimals = 4)
theme_set(theme_classic())
```

@@

cons_df_sum %>% 
  arrange(fm_consensus) %>% 
  select(Name, `Consensus pMC` = fm_consensus,
         `Mean pMC` = fm_corr_mean,
         `Mean pMC error` = sig_fm_corr_mean,
         `Std. dev. of measurements` = fm_corr_sd,
         N) %>% 
gt() %>% 
  tab_header(title = "Reference material precision and accuracy") %>% 
  fmt_number(2:5, 
             scale_by = 100,
             decimals = 2)
```

@@

cons_df %>% 
ggplot(aes(fm_consensus, fm_diff, color = Name)) + 
  geom_hline(yintercept = 0) +
  geom_hline(yintercept = mean_diff, color = "blue") +
  geom_hline(yintercept = mean_diff + sd_diff, color = "lightblue") +
  geom_hline(yintercept = mean_diff - sd_diff, color = "lightblue") +
  geom_smooth(method = "lm",  se = FALSE) + 
  geom_pointrange(aes(ymin = fm_diff - sig_fm_corr, 
                      ymax = fm_diff + sig_fm_corr), 
                  position = position_dodge2(width = 0.1), 
                  size = 0.5) + 
  scale_color_brewer(palette = "Dark2") +
  scale_x_continuous(labels = label_percent(suffix = "")) +
  scale_y_continuous(breaks = breaks_extended(7),
                     labels = label_percent(suffix = "",
                                            accuracy = 1)) +
  labs(title = "Agreement of HGIS with graphite measurements",
       subtitle = "Blank corrected HGIS measurements of consensus carbonate standards",
       x = "pMC expected (points jittered for clarity)", 
       y = "pMC difference (HGIS - expected)")
```

>>>>

```{r}
library(tidyverse)
library(amstools)
library(hgis)
library(here)
library(gt)
library(Bchron)
library(gghighlight)
library(patchwork)
library(scales)
library(latex2exp)
library(errors)

options(digits = 3)
options(scipen = 4)
options(decimals = 4)
options(errors.notation = "plus-minus")
theme_set(theme_classic())
```

@@

cons_df_sum %>% 
  arrange(fm_consensus) %>% 
  mutate(across(c(fm_consensus, fm_corr_mean, fm_corr_sd, sig_fm_corr_mean), 
         function(x) x * 100),
         fm_corr_err = set_errors(fm_corr_mean, fm_corr_sd)) %>% 
  select(Name, `Consensus` = fm_consensus,
         `HGIS ± SD` = fm_corr_err,
         #`HGIS` = fm_corr_mean,
         #`Std. dev. of measurements` = fm_corr_sd,
         `Mean per-sample error` = sig_fm_corr_mean,
         N) %>% 
gt() %>% 
  tab_header(title = "Reference material precision and accuracy",
             subtitle = "Values in pMC, Errors are SD of measurements") %>% 
  fmt_number(4, 
             decimals = 1) %>% 
  cols_align("right", 3)
```

@@

cons_df %>% 
ggplot(aes(fm_consensus, fm_diff, color = Name)) + 
  geom_hline(yintercept = 0) +
  geom_hline(yintercept = mean_diff, color = "blue") +
  geom_hline(yintercept = mean_diff + sd_diff, color = "lightblue") +
  geom_hline(yintercept = mean_diff - sd_diff, color = "lightblue") +
  geom_smooth(method = "lm",  se = FALSE) + 
  geom_pointrange(aes(ymin = fm_diff - sig_fm_corr, 
                      ymax = fm_diff + sig_fm_corr), 
                  position = position_dodge2(width = 0.1), 
                  ) + #size = 0.5) + 
   scale_color_brewer(palette = "Dark2") +
  # scale_color_manual(values = c("#00a9e0", "#0069b1", "#00b7bd", "#b7bf10", "#00b7bd")) +
  scale_x_continuous(labels = label_percent(suffix = "")) +
  scale_y_continuous(breaks = breaks_extended(7),
                     labels = label_percent(suffix = "",
                                            accuracy = 1)) +
  labs(title = "Agreement of HGIS with graphite measurements",
       subtitle = "Blank corrected HGIS measurements of consensus carbonate standards",
       x = "pMC expected (points jittered for clarity)", 
       y = "pMC difference (HGIS - expected)")
```
